Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-11-04 Thesis/chapter/061-results-emma.tex
results emma first good draft

\begin{figure}[hb]
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/stats/gen-G.png}
        \caption{} \label{fig:emma-G-gen}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/stats/gen-phd.png}
        \caption{} \label{fig:emma-phd-gen}
    \end{subfigure}
    \caption{Each $\gamma$ (a) and $\rho$ (b) of each particle and each generation after initial selection process} 
    \label{fig:emma-gen}
\end{figure}

%%% EQUATION 
Equations \ref{eq:emma-G3}-\ref{eq:emma-vcal3} and \ref{eq:emma-G4}-\ref{eq:emma-vcal4} represent the prediction functions at $t=3$ and $t=4$ rounded to 2 significant digits, respectively.
$h(x)$ is the hinge function (also called a rectifier function) of the simple form $h(x) = max(0,x)$. 
The expression $h(\lambda-6)$ translates into layer count only has an influence if larger than 6 
and $h(6-\lambda)$ into layer count influential only if under 6.
%
The first thing to notice is that every prediction function of a generation depends on the same variables. 
%This means that the algorithm must decide on the variables which explain the most variance independent of optimization weights.
This stems from the fact that the algorithm must chose a single minimal set of basis functions to predict all dependent variables. 
%
Knowing this, makes the decision of adding $\lambda$ and $v_{cal}$ as dependent variables rather unfortunate. %highly questionable. 
%As the \gls{mars} algorithm is gready,
Different independent variables compete to be in the prediction functions because of the greediness of the \gls{mars} algorithm. 
%\td{This makes including $\lambda$ and $v_{cal}$ as dependent variables unfortunate decisions with hindsight.}
In equations \ref{eq:emma-phd3} and \ref{eq:emma-G3} the coefficient have the same signs and differ by a factor of roughly 100.
This fits the data well, but the positive influence of the layer count/number is counter intuitive 
as one would expect more layers to be more insulating and thus result in lower conductance and a lower probability of pin holes going all the way trough the \gls{zro} layer. %pin hole density. 
The coefficients of the $v_{cal} \cdot T_{cal}$ interaction in equations \ref{eq:emma-phd3} and \ref{eq:emma-G3} 
seem low, but considering the minimum value of the inter action of \num{36000} should not be under estimated. 
%It's positive the hinge
It is astonishing that the knot of the hinge function for equations \ref{eq:emma-phd3}-\ref{eq:emma-vcal3} was chosen so low; 
basically only including the influence of $\lambda=4$.
On the positive site the calcination heating rate $v_{cal}$ (see equation \ref{eq:emma-vcal}) has been predicted perfectly within numerical precision.

For each generation the \gls{mse} was calculated such that only samples were used which were available at that time. 
It is 64, 158, 54 and 50 for $t=1,2,3,4$, respectively. 
The high \gls{mse} can be explained because the prediction function is only a constant at $t=2$. 
Appart from the second generation the \gls{mse} falls over time, which might be attributed to overfitting.
The \gls{mse} for each generation was calculated between predicted values for pre-optimisation samples to check for overfitting, 
but the the error sank with each generation (except for the second gen): 102, 118, 58, 50, respectively for $t=1,2,3,4$.

It is interesting that although prediction functions for $t=3$ perfectly predicted $v_{cal}$ 
the combined \gls{mse} for $t=4$ is lower. 
%%% MAIN INFLUENCE 
%Even without considering the large maximum of $T_{cal}$,

\iffalse
The coefficient for $T_{cal}$ is the largest for all equations. 
Factoring in the large maximum value of $T_{cal}$ in contrast the other independent variables, 
$T_{cal}$ has the by far the largest influence on the dependent variables. 
The coefficient of the interaction of $layr$ and $T_{cal}$ is about a tenth in size, %interaction between?H
but has the extra factor of $layr$ of up to 12, resulting in the products being in the same order of magnitude.
I can be noted that the coefficient of the $layr\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient. 
%%% EXPECTATION
It should be doubted, though, that the $layr$ only appears as interaction term 
together with $T_{cal}$ and $T_{DB}$, which seems rather than an artefact. 
\fi

\begin{align}
%
%    \label{eq:emma-phd1}
%    \hat{\rho}_1 &= -26  + 0.0025 \cdot T_{DB}\cdot T{Cal}  +  0.056 \cdot  h(6-\lambda)\cdot T_{Cal} \\
%    \label{eq:emma-G1}
%    \hat{\gamma}_1 &= -0.52 + 2.3\cdot 10^{-5} \cdot  T_{DB}\cdot T_{Cal} + 0.00080 \cdot h(6-layr)\cdot T_{cal}\\
%    \label{eq:emma-layr1}
%    \hat{\lambda}_1 &= 7.1 + 8.1\cdot 10^{-5} \cdot T_{DB}\cdot T_{cal} -  0.0056 \cdot  h(6-layr)\cdot T_{cal}\\
%    \label{eq:emma-vcal1}
%    \hat{v}_{cal,1} &= 19 - 0.00025 \cdot  T_{DB}\cdot T_{cal} - 0.0055 \cdot  h(6-layr)\cdot T_{cal}\\
%
%    \label{eq:emma-phd2}
%    \hat{\rho}_2 &= 47\\
%    \label{eq:emma-G2}
%    \hat{\gamma}_2 &= 0.23\\
%    \label{eq:emma-layr2}
%    \hat{\lambda}_2 &= 7.3\\
%    \label{eq:emma-vcal2}
%    \hat{v}_{cal,2} &= 10\\
%
    \label{eq:emma-phd3}
    \hat{\rho}_3 &= 0.075  -   0.0014 \cdot  v_{cal}  +    0.18 \cdot  h(6-\lambda)  + 3.9\cdot 10^{-06} \cdot  v_{cal}\cdot T_{cal} \\
    \label{eq:emma-G3}
    \hat{\gamma}_3 &= 43  -   0.097 \cdot  v_{cal}  +     10 \cdot  h(6-\lambda)  + 0.00026 \cdot  v_{cal}\cdot T_{cal} \\
    \label{eq:emma-layr3}
    \hat{\lambda}_3 &= 9.9  - 0.00064 \cdot  v_{cal}  -     2.7 \cdot  h(6-\lambda)  - 1.3\cdot 10^{-06} \cdot  v_{cal}\cdot T_{cal} \\
    \label{eq:emma-vcal3}
    \hat{v}_{cal,3} &= -5.2\cdot 10^{-15}  +   0.016 \cdot  v_{Cal}  + 1.3\cdot 10^{-15} \cdot  h(6-\lambda)  + 3.9\cdot 10^{-21} \cdot  v_{Cal}\cdot T_{cal} \\
%
    \label{eq:emma-phd4}
    \hat{\rho}_4 &=  -0.87 + 0.0047 \cdot  T_{cal} - 0.00036 \cdot  \lambda\cdot T_{cal}  +  0.0024 \cdot  h(\lambda-6)\cdot T_{DB} \\
    \label{eq:emma-G4}
    \hat{\gamma}_4 &=     -19 + 0.28 \cdot  T_{cal}  - 0.022 \cdot  \lambda\cdot T_{cal}  +  0.16 \cdot  h(\lambda-6)\cdot T_{DB} \\
    \label{eq:emma-layr4}
    \hat{\lambda}_4 &=  6.8 - 0.014 \cdot  T_{cal}  + 0.0018 \cdot  \lambda\cdot T_{cal}  + 0.0060 \cdot  h(\lambda-6)\cdot T_{DB} \\
    \label{eq:emma-vcal4}
    \hat{v}_{cal,4} &=  29 - 0.052 \cdot  T_{cal}  + 0.0011 \cdot  \lambda\cdot T_{cal}  -  0.011 \cdot  h(\lambda-6)\cdot T_{DB} 
\end{align}
%\fi
%what was the best result? For each particle there is best and global best.

%The calcination heating $v_{cal}$ rate has been predicted perfectly. 
%\td{even though $v_{cal}$ doesn't appear in the prediction function, how is this possible?}
%The number of layers $\lambda$ on the other hand was predicted poorly 
%even though the conversion factor was $1$ and the prediction function dependent on $\lambda$.

@@

%\iffalse
%\fi

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%\subsubsection{what is best}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{influence of variable selection on outcome}
The heating rate of the calcination process $v_{cal}$ and the number of layers $\lambda$ were included as dependent variable with the objective to maximize with a relative weight of 0.05 each.
The idea was to maximize $v_{cal}$ and minimize $\lambda$ in order to minimize the process time. 
Another thought behind including $v_{cal}$ and $\lambda$ was to test if the algorithm would correctly predict those. 
%
Three major flaws behind this consideration became obvious with time: 
%
\todo{
(1) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ ($C/h$ instead of $C/min$) and $\lambda$, respectively. 
The algorithm will tend to include those values into the prediction function for 
all dependent variables and possibly exclude others which have more influence 
on $\gamma$ and $\rho$ (see equations \ref{eq:emma-G} and \ref{eq:emma-phd}).
%
(2) The algorithm would be influenced by those values to choose samples, which potentially optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
%
(3) needlessly making the problem more complicate %, important time (around 10\% of the samples) could have been replaced with more insightful samples. 
\begin{itemize}
    \item MARS chooses same set from independent variables for predicting all dependent variables. 
    \item flaws of MARS: all functions are dependent on same independent vars
    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
heating rate was one of the dependent variables with the intention of minimizing the variable. 
It can also be used as test to see how well the EMMA performs (or rather, more precisely MARS)
It doesn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
Overall there were too many variables involved for such a small dataset
        that means that adding dependent variables influences \td{previous variables}
\end{itemize}
}

\td{look at emma papers}
\td{change G to gamma and write enr to every figure}
\td{calculate MSE for predictions}

>>>>

\begin{figure}[hb]
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/stats/gen-G.png}
        \caption{} \label{fig:emma-G-gen}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/stats/gen-phd.png}
        \caption{} \label{fig:emma-phd-gen}
    \end{subfigure}
    \caption{$\gamma$ (a) and of $\rho$ (b) of each particle and each generation after initial selection process} 
    \label{fig:emma-gen}
\end{figure}

%%% EQUATION 
%\subsubsection{Equation}
Equations \ref{eq:emma-phd3}-\ref{eq:emma-vcal3} and \ref{eq:emma-phd4}-\ref{eq:emma-vcal4} represent the prediction functions at $t=3$ and $t=4$ rounded to 2 significant digits, respectively.
$h(x)$ is the hinge function (also called a rectifier function) of the simple form $h(x) = max(0,x)$. 
The expression $h(\lambda-6)$ translates into layer count only has an influence if larger than 6 
and $h(6-\lambda)$ into layer count influential only if under 6.
%
The first thing to notice is that prediction functions of each generation depend on the same variables. 
%This means that the algorithm must decide on the variables which explain the most variance independent of optimization weights.
This stems from the fact that the algorithm must chose a single minimal set of \gls{bf} to predict all dependent variables. 
%
%\td{Knowing this, makes the decision of adding $\lambda$ and $v_{cal}$ as \textit{optimizands} rather unfortunate. %highly questionable. 
%\td{This makes including $\lambda$ and $v_{cal}$ as dependent variables unfortunate decisions with hindsight.}
%As the \gls{mars} algorithm is greedy,
%Different independent variables compete to be used as \gls{bf} in the prediction functions because of the greediness of the \gls{mars} algorithm. 
%}

\begin{align}
%
%    \label{eq:emma-phd1}
%    \hat{\rho}_1 &= -26  + 0.0025 \cdot T_{DB}\cdot T{Cal}  +  0.056 \cdot  h(6-\lambda)\cdot T_{Cal} \\
%    \label{eq:emma-G1}
%    \hat{\gamma}_1 &= -0.52 + 2.3\cdot 10^{-5} \cdot  T_{DB}\cdot T_{Cal} + 0.00080 \cdot h(6-layr)\cdot T_{cal}\\
%    \label{eq:emma-layr1}
%    \hat{\lambda}_1 &= 7.1 + 8.1\cdot 10^{-5} \cdot T_{DB}\cdot T_{cal} -  0.0056 \cdot  h(6-layr)\cdot T_{cal}\\
%    \label{eq:emma-vcal1}
%    \hat{v}_{cal,1} &= 19 - 0.00025 \cdot  T_{DB}\cdot T_{cal} - 0.0055 \cdot  h(6-layr)\cdot T_{cal}\\
%
%    \label{eq:emma-phd2}
%    \hat{\rho}_2 &= 47\\
%    \label{eq:emma-G2}
%    \hat{\gamma}_2 &= 0.23\\
%    \label{eq:emma-layr2}
%    \hat{\lambda}_2 &= 7.3\\
%    \label{eq:emma-vcal2}
%    \hat{v}_{cal,2} &= 10\\
%
    \label{eq:emma-phd3}
    \hat{\rho}_3 &= 0.075  -   0.0014 \cdot  v_{cal}  +    0.18 \cdot  h(6-\lambda)  + 3.9\cdot 10^{-06} \cdot  v_{cal}\cdot T_{cal} \\
    \label{eq:emma-G3}
    \hat{\gamma}_3 &= 43  -   0.097 \cdot  v_{cal}  +     10 \cdot  h(6-\lambda)  + 0.00026 \cdot  v_{cal}\cdot T_{cal} \\
    \label{eq:emma-layr3}
    \hat{\lambda}_3 &= 9.9  - 0.00064 \cdot  v_{cal}  -     2.7 \cdot  h(6-\lambda)  - 1.3\cdot 10^{-06} \cdot  v_{cal}\cdot T_{cal} \\
    \label{eq:emma-vcal3}
    \hat{v}_{cal,3} &= -5.2\cdot 10^{-15}  +   0.016 \cdot  v_{Cal}  + 1.3\cdot 10^{-15} \cdot  h(6-\lambda)  + 3.9\cdot 10^{-21} \cdot  v_{Cal}\cdot T_{cal} \\
%
    \label{eq:emma-phd4}
    \hat{\rho}_4 &=  -0.87 + 0.0047 \cdot  T_{cal} - 0.00036 \cdot  \lambda\cdot T_{cal}  +  0.0024 \cdot  h(\lambda-6)\cdot T_{DB} \\
    \label{eq:emma-G4}
    \hat{\gamma}_4 &=     -19 + 0.28 \cdot  T_{cal}  - 0.022 \cdot  \lambda\cdot T_{cal}  +  0.16 \cdot  h(\lambda-6)\cdot T_{DB} \\
    \label{eq:emma-layr4}
    \hat{\lambda}_4 &=  6.8 - 0.014 \cdot  T_{cal}  + 0.0018 \cdot  \lambda\cdot T_{cal}  + 0.0060 \cdot  h(\lambda-6)\cdot T_{DB} \\
    \label{eq:emma-vcal4}
    \hat{v}_{cal,4} &=  29 - 0.052 \cdot  T_{cal}  + 0.0011 \cdot  \lambda\cdot T_{cal}  -  0.011 \cdot  h(\lambda-6)\cdot T_{DB} 
\end{align}

The coefficients in equations \ref{eq:emma-phd3} and \ref{eq:emma-G3} have the same signs and differ by a factor of roughly 100.
This fits the data well, but the positive influence of the layer count/number is counter intuitive 
as one would expect more layers to be more insulating and thus result in lower conductance and a lower probability of holes going all the way trough the \gls{zro} layers. %pin hole density. 
The coefficients of the $v_{cal} \cdot T_{cal}$ interaction in equations \ref{eq:emma-phd3} and \ref{eq:emma-G3} 
seem low, but - considering the minimum value of the interaction of \num{36000} - have a higher influence on $\rho_3$ and $\gamma_3$ than $h(6 - \lambda)$. 
%It's positive the hinge
It is astonishing that the knot of the hinge function for equations \ref{eq:emma-phd3}-\ref{eq:emma-vcal3} was chosen so low; 
basically only including the influence of $\lambda=4$.
Meaning for equations \ref{eq:emma-phd3} and \ref{eq:emma-G3} that the lowest layer count produces worse samples which is intuitive, but more layers don't improve the insulation. 
On the positive side the calcination heating rate $v_{cal}$ (see equation \ref{eq:emma-vcal3}) has been predicted perfectly within numerical precision.

%%% T=4
The coefficient of equations \ref{eq:emma-phd4} and \ref{eq:emma-G4} show the same pattern 
as equations \ref{eq:emma-phd3} and \ref{eq:emma-G3}: identical signs and factor 100. 
The choice of \gls{bf} in combination with their coefficient signs of 
(\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) seem more plausible than (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
$\lambda$ decreases $G$ and $\rho$ and additionally the lowest $\lambda$ increases the two \textit{optimizands}. 
Highly interesting is the influence of $T_{cal}$ on the conductance of the sample. 
The conductance increases with higher calcination temperature, ergo the resistance decreases contrary to expectations.
It was expected that under \oc{400} the calcination does not fully \td{ablaufen} and 
that therefore the resulting layer does not insulate. 
Furthermore, the influence of $T_{cal}$ is the larges of all \gls{bf} on $\rho$ and $\gamma$.
%This becomes clear when looking at the data.
The coefficient of the interaction of $layr$ and $T_{cal}$ is about a tenth in size, 
but has the extra factor of $layr$ of up to 12, resulting in the products being in the same order of magnitude.
It can be noted that the coefficient of the $layr\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient. 
%It should be doubted, though, that the $layr$ only appears as interaction term 
%together with $T_{cal}$ and $T_{DB}$, which seems rather than an artefact. 
It seems rather an artefact of noise that the $\lambda$ only appears as interaction 
with $T_{cal}$ and $T_{DB}$.

%%% MSE
For each generation the \gls{mse} was calculated such that only samples 
from the optimisation were used which were available at the time of prediction. 
The \gls{mse} is 64, 158, 54 and 50 for $t=1,2,3,4$, respectively. 
It is interesting that although prediction functions for $t=3$ perfectly predicted $v_{cal}$ 
the combined \gls{mse} for $t=4$ is lower. 
The high \gls{mse} at $t=2$ can be explained because the prediction functions are only constant values. 
Apart from the second generation the \gls{mse} falls over time, which shows that the algorithm works but might be attributed to overfitting.
%The \gls{mse} for each generation was also calculated between predicted values for pre-optimisation samples to check for overfitting, 
The \gls{mse} for each generation's prediction function was also calculated with pre-optimisation samples, which are unseen data. 
The error sank again with each generation (except for the second generation): 102, 118, 58, 50, respectively for $t=1,2,3,4$. 
This means that the regularization method of the \gls{mars} algorithm in principle works on investigated samples. 
\td{It should be noted, that the validation \gls{mse} for $t=1$ is much higher.}
The high validation \gls{mse} (nearly 1.5 fold instead of circa 1 fold) for $t=1$ shows the poor prediction ability which improved.
\td{why is \gls{mse} higher with higher values? No homoscedasticity ( equality of variance)?
Or rather \gls{mse} at $t=2$ high because \gls{rf}s at $t=2$ poor and gen=2 samples are chosen with help of \gls{rf} at $t=2$? 
}

%%% PROBLEMS 
The two main problems were too many independent variables and too many dependent variables. 
Both seem closely related and overcomplicate the optimization but both come with their own implications. 
Too many independent variables make it harder to distinguish variance due to random error from variance due to dependency. 
This is mainly because of the curse of dimensionality \td{cite} which makes it hard to collect enough data for each dimension. 
The main problem about too many independent variables is that the same set of \gls{bf}s will be used to predict all \textit{optimizands}.
This leads to competition between the \gls{bf}s as not all dependent variables may depend on the same independent variables. 
This effect is reinforced by the choice of two independent variables as dependent variables (IVDV). 
Independent variables as dependent variables will likely be chosen in \gls{bf}s, 
for including them in the \gls{rf} is a easy way to reduce the \gls{mse}.
These \gls{bf}s then "take places" \td{(cf. musical chairs)} of \gls{bf}s predicting other dependent variables in the \gls{rf}. 
This in turn can lead to wrong predictions and therefore inefficient choice of future samples.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{rational behind including $v_{cal}$ and $\lambda$ as optimizands}
The heating rate of the calcination process $v_{cal}$ and the number of layers $\lambda$ 
were included as dependent variables with the objective to maximize with a relative weight of 0.05 each.
The idea was to maximize $v_{cal}$ and minimize $\lambda$ in order to minimize the process time. 
Another thought behind including $v_{cal}$ and $\lambda$ was to test if the algorithm would correctly predict those. 
%
%Three major flaws behind this consideration became obvious with time: 
%
\
\ds{
(1) The true function for predicting $v_{cal}$ and $\lambda$ are $v_cal*60$ (\oc{}/\h{} instead of \oc{}/\minutes{}) and $\lambda$, respectively. 
The algorithm will tend to include those values into the prediction function for 
all dependent variables and possibly exclude others which have more influence 
on $\gamma$ and $\rho$ (see equations \ref{eq:emma-G4}? and \ref{eq:emma-phd4}?).
%
(2) The algorithm would be influenced by those values to choose samples, which potentially optimize $v_{cal}$ and/or $\lambda$ but not $G$ or $\rho$. 
%
(3) needlessly making the problem more complicate %, important time (around 10\% of the samples) could have been replaced with more insightful samples. 
\begin{itemize}
    \item Every output var is independent of each other, so $v_{cal}$ can act as test 
heating rate was one of the dependent variables with the intention of minimizing the variable. 
It can also be used as test to see how well the EMMA performs (or rather, more precisely MARS).
Even if it didn't influence the fit for the other splines, but it influences the choice of samples therefore it might have slowed down the process
Overall there were too many variables involved for such a small dataset
        that means that adding dependent variables influences \td{previous variables}
\end{itemize}
}
\td{look at emma papers}
\td{change G to gamma and write enr to every figure}

@@

@@
